Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-07 paper/paper.tex
finalized musicnet description

We use training from sec.~\ref{sub:fitting_and_sparsification} with epochs lasting for $12$,
$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
stage. Preliminary experiments with the model without sparsification have shown that early
stopping almost always terminated the training process within the first $10-20$ epochs,
and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
epoch, used by \citet{trabelsi_deep_2017}. Besides stagewise training and shorter ``dense''
stage, other important deviations from their setup include:
\begin{itemize}
  \item shifting lower frequencies to the centre of the window to maintain locality after
  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_sparsification})
\end{itemize}
Each full three-stage experiment is replicated five times to take random effects into account,
e.g. random network initialization prior to ``dense'' stage, randomization of batches within
each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.

% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
% (do not mention that this was a mistake, you dummy!)

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Performance-compression frontier for the deep network of \citet{trabelsi_deep_2017}.
    Shaded horizontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model. \textbf{\color{blue} VD} and \textbf{\color{orange} ARD} denote
    methods \ref{ssub:variational_dropout}) ans \ref{ssub:empirical_bayes}, respectively.
    The \textbf{\color{pink} version} of the network with kernel $3$ in every convolution compressed with VD
    is (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

>>>>

Preliminary experiments with the model without sparsification have shown that early stopping
almost always terminated the training process within the first $10-20$ epochs, and that the
validation performance peaked at about $10-15$ epochs, much sooner than $200$ epochs used by
\citet{trabelsi_deep_2017}. Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs,
which essentially turns the ``dense'' stage into pretraining step. Early stopping, tracking
the validation split performance, is used only during the ``fine-tune'' stage. To keep the
learning rate schedule synchronised with such abbreviated training, we allow the base rate
of $10^{-3}$ to be scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$
and $\tfrac1{100}$, respectively. Other key deviations from the setup used by \citet{trabelsi_deep_2017}
include: shifting lower frequencies to the centre of the window to maintain locality after
applying FFT (sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of parameters'
gradients to $0.05$.

In each experiment we varied the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
Each full experiment is replicated five times to take random effects from network initialization
before ``dense'', stochastic batch sequence during SGD, and randomness of Bayesian forward
pass at ``sparsify'' stage.

Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier
for the deep network of \citet{trabelsi_deep_2017} and its version, in which we purposefully
halve the spatial size of the first $1d$ convolution kernel from $6$ to $3$ (denoted by
suffix \textit{k}$3$). The motivation is to test if the performance handicap introduced be
the forced compression of the most upstream layer can be alleviated through non-uniform
compression, induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout})
method in this sub-experiment, since prior results have not demonstrated significant difference
in performance-compression trade-off between VD and ARD (sec.~\ref{ssub:empirical_bayes}).

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}
    denote
    methods \ref{ssub:variational_dropout}) and \ref{ssub:empirical_bayes}, respectively.
    The \textbf{\color{pink} version} of the network with kernel $3$ in every convolution compressed with VD
    is (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

Shaded horizontal bands represent the min-max spread of the performance of the uncompressed
network upon termination of ``dense'' stage. Each point represents a precision-compression
value attained by a network after ``fine-tune'' stage. The end of the tail of each point
represents the performance gain or loss from the ``fine-tune'' stage itself.
%
For compression levels lower than $50$, the final stage overfits the network, since
undercompresed remain overparameterized. For rates higher than $\approx 100$ the ``fine-tune''
stage serves its purpose, essentially, due to the network's being sufficiently regularized
though sparsity. There is evidence in favour of achievability of the SOTA average precision
of \citet{trabelsi_deep_2017} within the $50$-$100$ compression region with $\cplx$-valued
automatic relevance derivative (sec.~\ref{ssub:empirical_bayes}).
